Country-Level Impact of Education on Entrepreneurship

### 2014-12-02 FromEducationToEntrepreneurship.Rmd
Created a map of Opportunity data and worked on cleaning WayofTeaching data

@@

#### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System

As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem. To do so, we decided to incorporate GEM indicators that relate to self-esteem and confidence. First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business. Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur. Both of these data sets indicate the average percentage for each characteristic at the country-level.

@@

GEM data was embedded in an interactive database and was difficult to extract automatically without writing a program. To simplify this process, we downloaded the necessary *.csv* files and saved them in our GitHub repository (to reduce complexity, we deleted the first three unnecessary rows before saving).  We then linked to the RAW version of the files and added the code required to load them from *R*.  The repmis package is required to load these documents from the repository.

Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analyzed.  In the process of doing this we created new data sets for each of these survey questions, which were called C*dataset* (clean followed by the data set name). This was done for each of the six GEM data sets before merging these sets two at a time to create the data set *FinalGEM*.

@@

# Obtain summary statistics of R3
summary(R3)
```

>>>>

(The impact of self confidence on entrepreneurship.)

@@

#### Key Explanatory Variable: Degree of Self-confidence Reinforcement within the Education System

As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem. To do so, we decided to incorporate GEM indicators that relate to self- confidence.  First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business. Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur. Both of these data sets indicate the average percentage for each characteristic at the country-level but they are solely describing a level of self-confidence in one's abilities to become an entrepreneur. We chose to use them as such even if they do not trace the specific causal chain between education systems and entrepreneurship that we intend to focus on.

In order to trace specifically how supportive of one's self-confidence a given education system is, we chose to use one specific item of the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection) as a proxy, namely D01.

"In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative"

Regarding this statement, the experts surveyed had to state whether it is:

1 completely false
2 somewhat false
3 neither true nor false
4 somewhat true
5 completely true

97 do not know
98 not applicable

@@

GEM data was embedded in an interactive database and was difficult to extract automatically without writing a programme. To simplify this process, we downloaded the necessary *.csv* files and saved them in our GitHub repository (to reduce complexity, we deleted the first three unnecessary rows before saving).  We then linked to the RAW version of the files and added the code required to load them from *R*.  The repmis package is required to load these documents from the repository.

Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analysed.  In the process of doing this we created new data sets for each of these survey questions, which were called C*dataset* (clean followed by the data set name). This was done for each of the six GEM data sets before merging these sets two at a time to create the data set *FinalGEM*.

@@

# Obtain summary statistics of R3
summary(R3)
